\documentclass[12pt]{extletter}

\usepackage{geometry}
\usepackage{soul}

% Adjust margins
\newgeometry{top=1cm, bottom=1cm}

% Adjust margins for aesthetics - Enlarging fornt size makes it look ugly
%\addtolength{\voffset}{-0.5in}
%\addtolength{\hoffset}{-0.3in}
\addtolength{\textheight}{2cm}

% Commenting the below line will push the closing "Sincerely," to the right of
% the page
\longindentation=0pt

% Your name for the signature at the bottom.
\signature{Saad Khan}
% Your address, phone number and e-mail address.
\address{29A Hollandale Lane \\
         Clifton Park, NY 12065 \\
         +1 (518) 389-5093 \\
         saad.khan02@gmail.com}
% Postion that you're applying for.
\newcommand{\jobPosition}{Automation Test Engineer}
% Company that you're applying to.
\newcommand{\companyName}{Verizon}

\begin{document}

\begin{letter}{}

\opening{\textbf{Vacancy: {\jobPosition}}}

I came across a vacancy for a {\jobPosition} at {\companyName} through
LinkedIn. I'm a Test Automation Engineer at Sixnet. Here my duties include
writing scripts for testing embedded Linux hardware and maintaining the test
infrastructure. I design and maintain the nightly tests and testing framework
that validate the software and hardware features of Remote Terminal Units and
the testing framework.

I also help maintain the test servers which run on Ubuntu 14.04. Most of the
testing is done on Linux using Perl and bash. Tests for Windows applications
are also integrated into the same framework using AutoIt and generating the
output in TAP (Test Anything Protocol) format. Tests are data driven (JSON)
in order to use the same framework for different platforms.

I believe I'll be a good fit for the available spot because of my attitude
towards the importance of testing. I have good experience in building and
integrating test frameworks. I'm a motivated team player and a go getter. I
hope to be an asset to the team if given the opportunity.

\vspace{2\parskip} % Extra whitespace for aesthetics
\closing{Sincerely,}
\vspace{2\parskip} % Extra whitespace for aesthetics

\end{letter}
 
\end{document}
